\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
summative procedure rewrite

\subsection{Procedure}
{\color {blue} 
Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random. When all participants sat at their respective computers,

With only the consenting participants remaining, one of the researchers then read from a script that details the experiment, task, and data collected (Appendix~\ref{quantitative-script}). We told users of the simulated censorship environment, that Tor Browser can be used to circumvent censorship, and that we ask them to use Tor Browser to circumvent our simulated censorship. We ask users to complete a worksheet, which asks questions that can only be answered by going to the censored websites. To mirror the qualitative study, we chose Wikipedia's featured article of the day as the blocked website to visit on their worksheet. All users were instructed to sit until the end of the experiment, regardless of when they had completed their task. We remind them again that their screens are being recorded and to not show any personal information, such checking email. We give users a chance to ask any questions about the experiment or task.

After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions. Participants had 40 minutes to complete the task. After the 40 minutes, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}) and were paid \$30 for their time. 
}

>>>>

\subsection{Procedure}
Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random. Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks. If they wished to participate, they were ifnormed again in writing and consented by signing the document. To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.

The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvnt censorship (Appendix~\ref{quantitative-script}). This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so. Before participants started their tasks, we reminded them that their screens are being recorded so they should not log into anything that shows personal information. We gave users a chance to ask any questions about the experiment or task.

Participants were given 40 minutes to complete the task. After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions. Afterward, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}). We paid each participant \$30 for their time.
